Real-world Feasibility Analysis of ACT Algorithm for Robotic Manipulation on Home

### 2025-05-17 paper.tex
fix:图表标题修改冒号改句号+标题后加句号

\usepackage{caption}   % 标题控制
\captionsetup[figure]{labelfont=bf} % 强制加粗编号
\captionsetup[table]{labelfont=bf} 
\newcolumntype{C}{>{\centering\arraybackslash}X} % 定义居中列类型
\usepackage{cleveref}
\crefformat{figure}{\textbf{Figure~#2#1#3}}

@@

 As shown in Fig.~\ref{fig1}(a),the algorithm employs action chunking and temporal ensemble techniques during training. With a fixed chunk size k, the agent receives environmental observations every k steps and executes k sequential actions. This design effectively reduces historical error accumulation. To ensure motion continuity, the algorithm queries the policy at every timestep, generating overlapping predicted actions that are then smoothly blended through temporal ensemble using exponential weighting.

\begin{figure}
\includegraphics[width=\textwidth]{fig1.pdf}
\caption{ACT implementation principles and CVAE model architecture}
\label{fig1}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=0.95\textwidth]{fig4.pdf}
  \caption{ initial state(upper left); target state(upper right);training environment(bottom)} \label{fig2}
  \end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{10}
\caption{Overall workflow}
 \label{fig10}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=323pt]{fig15.pdf}
\caption{The loss curve for the first two actions during model training} \label{fig14}
\end{figure}

@@

\begin{table}
  \centering
    \caption{\small Model training specifications}\label{tab2}
  \begin{tabularx}{\textwidth}{
      >{\centering\arraybackslash}p{0.8cm}     % 第一列固定宽度（窄）
      >{\centering\arraybackslash}X           % 第二列自动调整
      >{\centering\arraybackslash}X  
      >{\centering\arraybackslash}X           % 第四列自动调整
      >{\centering\arraybackslash}X           % 第五列自动调整
      >{\centering\arraybackslash}X           % 第六列自动调整
    }
\toprule
    \textbf{step} & \textbf{action} & \textbf{state} & \textbf{training time} & \textbf{episodes} & \textbf{success rate} \\
   \midrule
     1 & A --> B      & A[1234]-B[]-C[]       & 2h 7m 51s  & 90 & 9/10 \\
     2 & A --> C      & A[123]-B[4]-C[]       & 2h 14m 43s & 40 & 9/10 \\
     3 & B --> C      & A[12]-B[4]-C[3]       & 2h 11m 19s & 50 & 10/10 \\
     4 & A --> B      & A[12]-B[]-C[34]       & 3h 46m 55s & 40 & 10/10 \\
     5 & C --> A      & A[1]-B[2]-C[34]       & 2h 7m 44s  & 80 & 10/10 \\
     6 & C --> B      & A[14]-B[2]-C[3]       & 2h 24m 28s & 40 & 9/10 \\
     7 & A --> B      & A[14]-B[23]-C[]       & 4h 13m 50s & 40 & 9/10 \\
     8 & A --> C      & A[1]-B[234]-C[]       & 3h 13m 1s  & 40 & 10/10 \\
     9 & B --> C      & A[]-B[234]-C[1]       & 1h 59m 21s & 70 & 10/10 \\
     10 & B --> A     & A[]-B[23]-C[14]       & 1h 58m 55s & 60 & 10/10 \\
     11 & C --> A     & A[3]-B[2]-C[14]       & 2h 5m 1s   & 50 & 10/10 \\
     12 & B --> C     & A[34]-B[2]-C[1]       & 3h 2m 31s  & 40 & 9/10 \\
     13 & A --> B     & A[34]-B[]-C[12]       & 2h 0m 38s  & 60 & 10/10 \\
     14 & A --> C     & A[3]-B[4]-C[12]       & 3h 28m 24s & 40 & 9/10 \\
     15 & B --> C     & A[]-B[4]-C[123]       & 2h 11m 32s & 70 & 10/10 \\
     \bottomrule
  \end{tabularx}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[width=323pt]{fig8.pdf}
\caption{Loss curve} \label{fig19}
\end{figure}

>>>>

\usepackage{caption}
\captionsetup{
    labelfont=bf,    % 加粗标签
    labelsep=period, % 强制使用句点(.)而不是冒号(:)
}

\newcolumntype{C}{>{\centering\arraybackslash}X} % 定义居中列类型
\usepackage{cleveref}
\crefformat{figure}{\textbf{Figure~#2#1#3}}

@@

 As shown in Fig.~\ref{fig1}(a), the algorithm employs action chunking and temporal ensemble techniques during training. With a fixed chunk size k, the agent receives environmental observations every k steps and executes k sequential actions. This design effectively reduces historical error accumulation. To ensure motion continuity, the algorithm queries the policy at every timestep, generating overlapping predicted actions that are then smoothly blended through temporal ensemble using exponential weighting.

\begin{figure}
\includegraphics[width=\textwidth]{fig1.pdf}
\caption{ACT implementation principles and CVAE model architecture.}
\label{fig1}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=0.95\textwidth]{fig4.pdf}
  \caption{ initial state(upper left); target state(upper right);training environment(bottom).} \label{fig2}
  \end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{10}
\caption{Overall workflow.}
 \label{fig10}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=323pt]{fig15.pdf}
\caption{The loss curve for the first two actions during model training.} \label{fig14}
\end{figure}

@@

\begin{table}
  \centering
    \caption{Model training specifications}\label{tab2}
  \begin{tabularx}{\textwidth}{
      >{\centering\arraybackslash}p{0.8cm}     % 第一列固定宽度（窄）
      >{\centering\arraybackslash}X           % 第二列自动调整
      >{\centering\arraybackslash}X  
      >{\centering\arraybackslash}X           % 第四列自动调整
      >{\centering\arraybackslash}X           % 第五列自动调整
      >{\centering\arraybackslash}X           % 第六列自动调整
    }
\toprule
    \textbf{step} & \textbf{action} & \textbf{state} & \textbf{training time} & \textbf{episodes} & \textbf{success rate} \\
   \midrule
     1 & A --> B      & A[1234]-B[]-C[]       & 2h 7m 51s  & 90 & 9/10 \\
     2 & A --> C      & A[123]-B[4]-C[]       & 2h 14m 43s & 40 & 9/10 \\
     3 & B --> C      & A[12]-B[4]-C[3]       & 2h 11m 19s & 50 & 10/10 \\
     4 & A --> B      & A[12]-B[]-C[34]       & 3h 46m 55s & 40 & 10/10 \\
     5 & C --> A      & A[1]-B[2]-C[34]       & 2h 7m 44s  & 80 & 10/10 \\
     6 & C --> B      & A[14]-B[2]-C[3]       & 2h 24m 28s & 40 & 9/10 \\
     7 & A --> B      & A[14]-B[23]-C[]       & 4h 13m 50s & 40 & 9/10 \\
     8 & A --> C      & A[1]-B[234]-C[]       & 3h 13m 1s  & 40 & 10/10 \\
     9 & B --> C      & A[]-B[234]-C[1]       & 1h 59m 21s & 70 & 10/10 \\
     10 & B --> A     & A[]-B[23]-C[14]       & 1h 58m 55s & 60 & 10/10 \\
     11 & C --> A     & A[3]-B[2]-C[14]       & 2h 5m 1s   & 50 & 10/10 \\
     12 & B --> C     & A[34]-B[2]-C[1]       & 3h 2m 31s  & 40 & 9/10 \\
     13 & A --> B     & A[34]-B[]-C[12]       & 2h 0m 38s  & 60 & 10/10 \\
     14 & A --> C     & A[3]-B[4]-C[12]       & 3h 28m 24s & 40 & 9/10 \\
     15 & B --> C     & A[]-B[4]-C[123]       & 2h 11m 32s & 70 & 10/10 \\
     \bottomrule
  \end{tabularx}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[width=323pt]{fig8.pdf}
\caption{Loss curve.} \label{fig19}
\end{figure}
